---
title: "SimBenchData: a collection of 35 single-cell RNA-seq data covering a wide range of data characteristics"
author:
- name: Yue Cao
  affiliation: School of Mathematics and Statistics, University of Sydney; Charles Perkins Centre, University of Sydney, Sydney, NSW, Australia
  email: yue.cao@sydney.edu.au
- name: Pengyi Yang
  affiliation: School of Mathematics and Statistics, University of Sydney, Sydney, NSW, Australia;   Charles Perkins Centre, University of Sydney, Sydney, NSW, Australia;   Computational Systems Biology Group, Children's Medical Research Institute, University of Sydney, Westmead, NSW, Australia
  email: pengyi.yang@sydney.edu.au
- name: Jean Yee Hwa Yang
  affiliation: School of Mathematics and Statistics, University of Sydney; Charles Perkins Centre, University of Sydney, Sydney, NSW, Australia
  email: jean.yang@sydney.edu.au
package: SimBenchData
output:
  BiocStyle::html_document
vignette: |
  %\VignetteIndexEntry{SimBenchData: a collection of single-cell RNA-seq data covering a wide range of data characteristics}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
 
# Introduction

The SimBenchData package contains a total of 35 single-cell RNA-seq datasets covering a wide range of data characteristics, including major sequencing protocols, multiple tissue types, and both human and mouse sources. This package serves as a key resource for performance benchmark of single-cell simulation methods, and was used to comprehensively assess the performance of 12 single-cell simulation methods in retaining key data properties of single-cell sequencing data, including gene-wise and cell-wise properties, as well as biological signals such as differential expression and differential proportion of genes. This data package is a valuable resource for the single-cell community for future development and benchmarking of new single-cell simulation methods and other applications. 


# The SimBenchData dataset 

The data stored in this package can be retrieved using ExperimentHub.   

```{r warning=FALSE, message=FALSE}
# if (!requireNamespace("BiocManager", quietly = TRUE))
#     install.packages("BiocManager")
# 
# BiocManager::install("ExperimentHub")

library(ExperimentHub)
eh <- ExperimentHub()
alldata <- query(eh, "SimBenchData")
alldata 
```

Each dataset can be downloaded using its ID. 
```{r eval=FALSE, include=TRUE}
data_1 <- alldata[["EH5384"]]  
```

Information about each dataset such as its description and source URL can be found in the metadata files under the `inst/extdata` directory. It can also be explored using the function `showMetaData`. Additional details on each dataset can be explored using the function `showAdditionalDetail()`. The information on the first three datasets is shown as an example.   


```{r}
library(SimBenchData)

metadata <- showMetaData()
metadata[1:3, ]

additionaldetail <- showAdditionalDetail()
additionaldetail[1:3, ]
```


The data processing script for each dataset can be found under the `inst/scripts` directory.     



# Session info {.unnumbered}

```{r sessionInfo, echo=FALSE}
sessionInfo()
```
